Lemma 1

### 2021-04-28 notes/jessie-russian-lemma.tex
Updating section 3 if we're okay with complete measures.

Consider a sequence $\{v_m\} \to v$ such that $v_m \in A$ for all $m$.  We have (by part 1 of the lemma) selections $V_m$ such that $v_m = \E_p V_m$ and the $v_m$ has bounded norm.
If we have $v \in A$, then we have $A \supseteq cl(A)$, and therefore $A$ closed.

Now define functions $P_m : 2^\Y \to \reals^d$ so that $P_m(E) = \int_E V_m(y) dpy$.  
We can use Helly's Theorem (Theorem~\ref{thm:helly}?) to claim that $P_m$ converges pointwise to some function $P$ of bounded variation.\jessie{We need montonicity of the functions $P_m$, but is this definition $A \subseteq B \implies f(A) \leq f(B)$?}
We have uniform boundedness from their first past of the result, and monotonicity from the nonnegativity of probability densities. \jessie{Nope}%from each $P_m$ being a CDF.

@@

This yields $P(\sup_{y' \in \Y} y) = \int V(y) dy \in \int \partial L(u,y) dpy$.

@@

\section{Zooming out: revisiting Rockafellar Wets}
Rockafellar and Wets define expectation of a multifunction as 
\begin{align*}
A &= \E_p \partial L(u,Y) &= cl\{\E_p V \mid V(y) \in \partial L(u,y) p-a.s. \}
\end{align*}
%written 17 April. commented out 18 April with new verison
%Let's think about the same set as before, but take the closure first.
%\begin{align*}
%Z &= cl\{\E_p V \mid V \in \V_u\}
%\end{align*}
%Let's show $Z$ yields a selection $V$ such that (a) $V \in \V_u$, (b) $\E_p V = \vec 0$.
%Applying the Aliprantis Border result, we have (a) with more info than we need, but know that $V$ is measurable.  
%If $V$ is in the boundary of $Z$, consider that there is a sequence of measurable functions in $Z$ that converges to $V$ pointwise almost everywhere, and therefore $V$ is measurable as well. \jessie{check claim??}
%
%Moreover, we can apply the DCT to show that $\E_p V = 0$, as it is the limit of a sequence of measurable functions in $Z$ s.t. $E_p V_m = \vec 0$.?
%\jessie{Need to show $\vec 0 \in \E_p \partial L(u,Y) = cl\{\E_p V \mid V(y) \in \partial L(u,y) p-a.s. \} \implies \vec 0 \in Z$}.
%If $0 \not \in Z$, then there are some sets $E_1, E_2 \subseteq \Y$ such that $V(y) \neq \partial L(u,y)$ for all $y \in E_1$ and $E_2$.
%However we claim $p(E_1) = 0$ and $p(y) = 0$ for all $y \in E_2$.
%Therefore, 
%
%
%
%We then have $V$ measurable and $q \in \ker_\P V \implies \E_q V = \vec 0 \implies \vec 0 \in \E_p \partial L(u,Y) = \partial \E_p L(u,Y) \implies u \in \Gamma(q) \implies q \in \Gamma_u$.
%Thus the proof is complete.

%new 18 Apr 21
Consider the set $Z = \{\E_p V \mid V \in \V_u\}$.
We claim that $Z = A$.
$Z \subset A$ is trivial, so it is left to show $A \subseteq Z$.

Consider $v \in A$.
There is a sequence $\{v_m\} \to v$ such that $v_m \in A$, and therefore there is a sequence $V_m$ of measurable functions in the subgradient set of $L(u,y)$ $p$-almost surely.
\jessie{Claim: $V_m \to V$, $V$ is measurable, and $\E_p V = v$.  The second is true if $V_m \to V$ pointwise almost everywhere. And third should follow as well from convergence and DCT?}

Now consider $E = \{y \in \Y \mid V(y) \in \partial L(u,y)\}$.
We have $p(E^c) = 0$ and $E \in$ the sigma algebra by definition of $p$-almost surely.
Therefore $E^c$ is in the sigma algebra.
Therefore, for all $y \in E^c$, we can set $V'(y) = 0$ and $V'(y) = V(y)$ for $y \in E$.
We have $V'$ measurable as $V'^{-1}(\{0\}) = E^c \cup \{x \mid V(x) = 0\}$, which is the union of elements of the sigma algebra, and therefore is also in the sigma algebra.  
Therefore we have
\begin{align*}
v &= \lim_{m \to \infty} v_m\\
&= \lim_{m \to \infty} \int_\Y V_m\\
&= \int_\Y V(y) dpy \jessie{DCT}\\
&= \int_{E} V(y) dpy + \int_{E^c} V(y) dpy\\
&= \int_{E} V(y) dpy\\
&= \int_{E} V'(y) dpy\\
&= \int_{E} V'(y) dpy + \int_{E^c} V'(y) dpy \\
&= \int_\Y V'(y)
\end{align*}

Therefore, $v \in Z$.

>>>>

Consider a sequence $\{v_m\} \to v$ such that $v_m \in A$ for all $m$.  We have (by part 1 of the lemma) measurable selections $V_m$ such that $v_m = \E_p V_m$ and the $v_m$ has bounded norm.
If we have $v \in A$, then we have $A \supseteq cl(A)$, and therefore $A$ closed.

Now define functions $P_m : 2^\Y \to \reals^d$ so that $P_m(E) = \int_E V_m(y) dpy$.  
We can use Helly's Theorem (Theorem~\ref{thm:helly}?) to claim that $P_m$ converges pointwise to some function $P$ of bounded variation.\jessie{We need montonicity of the functions $P_m$, but is this definition $A \subseteq B \implies f(A) \leq f(B)$? We don't have that.}
We have uniform boundedness from their first past of the result, and monotonicity from the nonnegativity of probability densities. \jessie{Nope}%from each $P_m$ being a CDF.

@@

This yields $P(\Y) = \int_\Y V(y) dpy \in \int_\Y \partial L(u,y) dpy$.

@@

\section{Zooming out: complete measures}
We are working on the measure space $(\Omega, B)$ with probability measure $p$.

Ioffe and Tikhomirov define expectation of a multifunction as 
\begin{align*}
A = \E_p \partial L(u,Y) &= \{\E_p V \mid V(y) \in \partial L(u,y) p-a.s. \}
\end{align*}
%written 17 April. commented out 18 April with new verison
%Let's think about the same set as before, but take the closure first.
%\begin{align*}
%Z &= cl\{\E_p V \mid V \in \V_u\}
%\end{align*}
%Let's show $Z$ yields a selection $V$ such that (a) $V \in \V_u$, (b) $\E_p V = \vec 0$.
%Applying the Aliprantis Border result, we have (a) with more info than we need, but know that $V$ is measurable.  
%If $V$ is in the boundary of $Z$, consider that there is a sequence of measurable functions in $Z$ that converges to $V$ pointwise almost everywhere, and therefore $V$ is measurable as well. \jessie{check claim??}
%
%Moreover, we can apply the DCT to show that $\E_p V = 0$, as it is the limit of a sequence of measurable functions in $Z$ s.t. $E_p V_m = \vec 0$.?
%\jessie{Need to show $\vec 0 \in \E_p \partial L(u,Y) = cl\{\E_p V \mid V(y) \in \partial L(u,y) p-a.s. \} \implies \vec 0 \in Z$}.
%If $0 \not \in Z$, then there are some sets $E_1, E_2 \subseteq \Y$ such that $V(y) \neq \partial L(u,y)$ for all $y \in E_1$ and $E_2$.
%However we claim $p(E_1) = 0$ and $p(y) = 0$ for all $y \in E_2$.
%Therefore, 
%
%
%
%We then have $V$ measurable and $q \in \ker_\P V \implies \E_q V = \vec 0 \implies \vec 0 \in \E_p \partial L(u,Y) = \partial \E_p L(u,Y) \implies u \in \Gamma(q) \implies q \in \Gamma_u$.
%Thus the proof is complete.

%new 18 Apr 21
Consider the set $Z = \{\E_p V \mid V \in \V_u\}$.
We claim that $Z = A$.
$Z \subseteq A$ is trivial, so it is left to show $A \subseteq Z$.

Consider $v \in A$.
There is some measurable function $V$ such that $\E_p V = v$ such that $V(y) \in \partial L(u,y)$ almost surely in $p$; we want to modify $V$ into $V' \in\Z$ so that $\E_p V = \E_p V'$, and $V'$ is still measurable.

Now consider $E = \{y \in \Y \mid V(y) \in \partial L(u,y)\}$.
We have $p(E^c) = 0$ and $E \in B$ by definition of $p$-almost surely.
Therefore $E^c \in B$.
Moreover, since $p$ is a complete measure, every $N \subseteq E^c\in B$.

Therefore, we can take $V'$ to be any function that matches $V$ on $y \in E$, and takes any $V'(y) \in \partial L(u,y)$ (which is nonempty and compact by minnability and finiteness of $L$, respectively) elsewhere. \jessiet{Not sure if we want something explicit, but wasn't sure how to define it to be unique.  Mostly was thinking about minning the norm, but still needs more specificity.}
As $V$ is measurable and $p$ is a complete measure, we have $V'$ measurable.
Consider that for all $x \in \reals^d$, we have $V'^{-1}(x) = V^{-1}(x) \cup \{y \in E^c : V'(y) = x\}$.
As $V$ is measurable, we have $V^{-1}(x) \in B$ and since $p$ is a complete measure, we know that $\{y \in E^c : V'(y) = x\} \in B$ as well.
Since sigma algebras are closed under finite unions, we have $V'^{-1}(x) \in B$ for all $x$, and therefore $V'$ is measurable.

%, for all $y \in E^c$, we can set $V'(y) = 0$ and $V'(y) = V(y)$ for $y \in E$. \jessie{Need to have $V'(y) \in \partial L(u,y)$}
%We have $V'$ measurable as $V'^{-1}(\{0\}) = E^c \cup \{x \mid V(x) = 0\}$, which is the union of elements of the sigma algebra, and therefore is also in the sigma algebra.  
Moreover, we have
\begin{align*}
v &= \int_\Y V(y) dpy \\
&= \int_{E} V(y) dpy + \int_{E^c} V(y) dpy\\
&= \int_{E} V(y) dpy\\
&= \int_{E} V'(y) dpy\\
&= \int_{E} V'(y) dpy + \int_{E^c} V'(y) dpy \\
&= \int_\Y V'(y) dpy~,~
\end{align*}
and thus $v = \E_p V = \E_p V'$, so $v \in Z$.
Therefore, $v \in Z$, so $A \subseteq Z$.
